Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-12 paper.tex
update

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing. This accomplishment has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which is designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. Several standards play a significant role in registering, enquiring and grounding web services including particularly UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increase in the number of large-scale enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge $(1)$ in the dimensions of syntactic and semantics \cite{fensel2011semantic}. The syntactic dimension is covered the XML-based technologies (such as $WSDL$, $SOAP$). The semantics aspect, on the other hand, demands further research. Through semantics given by ontologies \cite{o2005review}, web services understand and better collaborate with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}. The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$) over composite web services. This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition focus mainly addressing two challenges above. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. However, customers often prefer a service composition that matches their requirement most with highest QoS.

@@

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity. This approach is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.

 \item To propose a PSO-based service composition model that utilise the proposed quality model. In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition in the searching space, which are decoded from an optimised service queue with the consideration of comprehensive quality.

@@

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused mainly on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both addressed both of them at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} are the papers could be found so far. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking. It is considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.

In \cite{shet2012new}, three approaches are surveyed three approaches regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$. A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied for the degree of similarity using Common Description rate of a semantic link, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated. They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$.

However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2. This makes it difficult to measure semantic matchmaking quality in most semantic web services applications, as it takes unpredictable cost and time for the domain experts to establish required ontology. Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method. Only cost and time are considered in the optimised problems. Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.

In \cite{fanjiang2014semantic}, it covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns. In details, a sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality. Apart from that, match types are ignored in their quality evaluation of semantic matching.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique to solve automated web service composition. This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as particles in their PSO algorithm considering QoS optimisation. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as a different semantic web service composition representations from \cite{da2016particle}.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composite goal, a combination of web services will be found to meet $Comp.G$. To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$. A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an Ontology (O). To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}. To understand these levels, let us define two web services associated with concept-related parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S_{2}$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$. The matching levels to be considered are:

@@

Note that, to find relevant services for service compositions according to a given goal, we consider Exact, Plugin, Subsume and Fail match types in our paper. Therefore, these matches will be used to discover web service candidates for service composition in our proposed the comprehensive quality-aware model in Sect.\ref{semantic_matchmaking}

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements. This problem has been explored in both single objective and multi-objectives optimisation problems. Customers prefer lowest execution cost with highest response time and reliability so that it could be involved as a single objective optimisation problem while cost and reliability of web service are two conflicting objectives that could be optimised simultaneously in multi-objective problem. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other in a service composition \cite{zeng2003quality}. Here we consider two composite constructs: sequence and parallel constructs, in building the composite flow. The QoS calculation models are described as follows:

@@

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed in the meantime. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution. This construct is presented in Fig. \ref{parallel}.

\section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered as graph vertices while edges are assigned with semantic matchmaking quality as weights. Step 4,5: The selection of web services performs PSO algorithm in Sect. \ref{pso_algorithm} to find best particle location. This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation while considering a comprehensive quality for optimisation problem.

\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match demonstrated in Sect. \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the mode model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfies the quality of QoS with considering its functional quality.

The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services. In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL, MECE is considered to be an alternative semantic annotation for WSDL. MECE defines the service-related inputs and outputs with parameter-related concepts. OWL-DL is a sublanguage of OWL from extension of RDF. which specifies semantic information of concepts involved in MECE.

\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive}.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the semantic matchmaking quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy-based measurement for ontology matching. This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services. Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {matchType})$ is set up as the same as that in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

Further more, edges represent services connections in our weighted graph presentations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations. The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {matchType})$ and $q(e_ {similarity})$ are the average value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.

@@

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of a goal. The comprehensive quality of our service composition representation refers to QoS of service vertices and Semantic matching quality of Edges in weighted graphs. Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}). 
\begin{equation}
\label{equation4}
q_{cq} \stackrel{.}{=} (q(e_ {sm}), \  q(v_ {QoS}))
\end{equation}
\begin{equation}
\label{equation5}
q_{cq} \stackrel{.}{=} (q(e_ {mt}), \  q(e_ {s}), \  q(v_{a}),\  q(v_{r}),\  q(v_{c}),\  q(v_{t}))
\end{equation}

\textbf{Quality aggregate matrix}. The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties. The quality on construct level is further calculated and by following the rules summarised in Table \ref{table1}.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as $WG = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which is described in the Fig. \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$ assigned as weights.

>>>>

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) is capable of abstractly realising service-oriented paradigm of computing. Since its inception, SOA has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which is designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. Several standards play a significant role in registering, enquiring and grounding web services including particularly UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increase in the number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions \cite{fensel2011semantic}. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantics aspect, on the other hand, demands further research. Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}. The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$) over composite web services. This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition focus mainly on addressing the two challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach. Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are deemed to NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. However, customers often prefer a service composition that best matches their requirement with highest QoS.

@@

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding semantic similarity. This approach is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.

 \item To propose a PSO-based service composition algorithm that utilises the proposed quality model. In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition in the searching space, and the weighted graph solutions are decoded from an optimised service queue with the consideration of the proposed comprehensive quality.

@@

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} reported some recent attempts over published. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking. It is considered to be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology.

In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$. A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied to the degree of similarity using Common Description rate of a semantic link, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated. They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$. However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2. This makes it difficult to measure semantic matchmaking quality in most available semantic web services, as it takes huge cost and time for the domain experts to establish required ontology. In comparison, we introduce a more applicable comprehensive quality model in a fully automated approach.

The paper \cite{fanjiang2014semantic} covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns. In details, a sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality. Apart from that, match types are ignored in their quality evaluation of semantic matching.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problems. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique for automated web service composition. This GP-based approach utilises tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation. However, this solution does not consider distinguished matchmaking quality, which could lead to over-general outputs to be produced by selected services. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter similarity to determine the overall quality of web service composition. Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part focus on transfering a given task input or input set to the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composite goal, a combination of web services will be found to meet $Comp.G$. To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository in view of customers' functional requests. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$. A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an Ontology (O). To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}. To understand these levels, let us define two web services associated with concept-related parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S_{2}$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$. The matching levels to be considered are:

@@

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements. This problem has been explored in both single objective and multi-objectives optimisation problems. Customers prefer lowest execution cost with highest response time and reliability that could be optimised simultaneously. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}. Here we consider two composite constructs: sequence and parallel constructs, in building the composite web service. The QoS calculation models are described as follows:

@@

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed concurrently. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composite flow of the solution. This construct is presented in Fig. \ref{parallel}.

\section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.

\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match demonstrated in Sect. \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the quality model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfy the quality of QoS with good functional quality.

The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services. In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL. MECE is considered to be an alternative semantic annotation for WSDL. MECE defines the service-related inputs and outputs with parameter-related concepts. OWL-DL is a sublanguage of OWL extended from RDF. It specifies semantic information of concepts involved in MECE.

\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} that ignores quality of semantic matchmaking.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for the semantic matchmaking quality. For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services. Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {mt})$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

Further more, edges represent services connections in our weighted graph representations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations. The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {mt})$ and $q(e_ {s})$ are the average value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.

@@

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements. The comprehensive quality of our service composition representation refers to QoS of service vertices and Semantic matching quality of Edges in weighted graphs. Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}). 
\begin{equation}
\label{equation4}
q_{cq} \stackrel{.}{=} (q(e_ {sm}), \  q(v_ {QoS}))
\end{equation}
\begin{equation}
\label{equation5}
q_{cq} \stackrel{.}{=} (q(e_ {mt}), \  q(e_ {s}), \  q(v_{a}),\  q(v_{r}),\  q(v_{c}),\  q(v_{t}))
\end{equation}

\textbf{Quality aggregate matrix}. The quality aggregation is defined based on the constructs of composite web services, in consideration of functional and non-functional properties. The quality on construct level is further calculated by following the rules summarised in Table \ref{table1}.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which is described in Fig. \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$ assigned as weights.
